**The Role of Interoception and Theory of Mind in Deception**

### 2022-11-21 2_ManipulationChecks.Rmd
anonimize data and revise ms

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

@@

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

@@

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

>>>>

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Answer")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
```

@@

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
modelbased::estimate_contrasts(model, contrast = "Condition")
```

@@

```{r message=FALSE, warning=FALSE}
modelbased::estimate_contrasts(model, contrast = "Answer", at = "Condition")
modelbased::estimate_contrasts(model, contrast = "Answer")
modelbased::estimate_contrasts(model, contrast = "Condition", at = "Answer")
modelbased::estimate_contrasts(model, contrast = "Condition")
```

### 2022-11-21 index.Rmd
anonimize data and revise ms

```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data_combined.csv") %>% 
  mutate(Participant = factor(paste0("S", Participant), levels = paste0("S", 1:30)),
         Condition = as.factor(Condition),
         Item = as.factor(Item),
         Phrasing = as.factor(Phrasing),
         Answer = as.factor(Answer)) |> 
  dplyr::filter(!Participant %in% c("S3", "S15", "S19", "S23"))  # No data

@@

p1 <- ggplot(link_data, aes(x = ToM, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = ToM_Mean,
                      xend = ToM_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = ToM_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(ToM = -0.3, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = "Theory of Mind") +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p1

@@

p2 <- ggplot(link_data, aes(x = Intero_Meta, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Meta_Mean,
                      xend = Intero_Meta_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Meta_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Meta = -0.15, Predicted = 0.25, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception["  (.97 MAIA Attention regulation, .63 MAIA Self-regulation, .60 MAIA Emotional Awareness)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p2

@@

p3 <- ggplot(link_data, aes(x = Intero_Listening, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Listening_Mean,
                      xend = Intero_Listening_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Listening_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Listening = 0.2, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception["  (.92 MAIA Body listening, -.60 HCT Awareness, .53 HCT Trusting)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))

@@

p4 <- ggplot(link_data, aes(x = Intero_Focus, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Focus_Mean,
                      xend = Intero_Focus_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Focus_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Focus = -0.2,
                            Predicted = c(0.55, 0.75),
                            Condition = c("Polygraph", "Interrogation"),
                            Answer = c("Truth", "Truth")),
            label = c("*", "*"),
            color = c("#2196F3", "#FF5722"),
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception["  (.87 MAIA Not-distracting, -.40 MAIA Emotional Awareness, .33 HCT Accuracy)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p4

@@

p5 <- ggplot(link_data, aes(x = Intero_Regulation, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Regulation_Mean,
                      xend = Intero_Regulation_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Regulation_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Regulation = -0.15, 
                            Predicted = c(0.25, 0.45, 0.75),
                            Condition = c("Polygraph", "Interrogation", "Polygraph"), 
                            Answer = c("Lie", "Lie", "Truth")),
            label = c("***", "*", "*"),
            color = c("#FF5722", "#2196F3", "#FF5722"),
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception["  (.71 MAIA Not-worrying, .61 HCT Accuracy, .40 MAIA Trusting)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white")) 
p5

>>>>

```{r warning=FALSE, message=TRUE, results='asis'}
df <- read.csv("data/data.csv")

@@

p1 <- ggplot(link_data, aes(x = ToM, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = ToM_Mean,
                      xend = ToM_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = ToM_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(ToM = -0.3, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Theory~of~Mind~"'Composite'"["  (.89 YONI Cognitive, .77 YONI Affective, .45 YONI Physical)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p1

@@

p2 <- ggplot(link_data, aes(x = Intero_Meta, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Meta_Mean,
                      xend = Intero_Meta_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Meta_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Meta = -0.15, Predicted = 0.25, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception~"'Meta'"["  (.97 MAIA Attention regulation, .63 MAIA Self-regulation, .60 MAIA Emotional Awareness)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p2

@@

p3 <- ggplot(link_data, aes(x = Intero_Listening, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Listening_Mean,
                      xend = Intero_Listening_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Listening_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Listening = 0.2, Predicted = 0.45, Condition = "Polygraph", Answer = "Lie"),
            label = "***",
            color = "#FF5722",
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception~"'Listening'"["  (.92 MAIA Body listening, -.60 HCT Awareness, .53 HCT Trusting)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))

@@

p4 <- ggplot(link_data, aes(x = Intero_Focus, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Focus_Mean,
                      xend = Intero_Focus_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Focus_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Focus = -0.2,
                            Predicted = c(0.55, 0.75),
                            Condition = c("Polygraph", "Interrogation"),
                            Answer = c("Truth", "Truth")),
            label = c("*", "*"),
            color = c("#2196F3", "#FF5722"),
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception~"'Focus'"["  (.87 MAIA Not-distracting, -.40 MAIA Emotional Awareness, .33 HCT Accuracy)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white"))
p4

@@

p5 <- ggplot(link_data, aes(x = Intero_Regulation, y = Predicted)) +
  geom_segment(data = data,
                  aes(x = Intero_Regulation_Mean,
                      xend = Intero_Regulation_Mean,
                      y = Confidence_low,
                      yend = Confidence_high,
                      color = Condition),
                  alpha=1/3) +
  geom_point2(data = data,
                  aes(x = Intero_Regulation_Mean,
                      y = Confidence_Mean,
                      color = Condition),
              size=2) +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 1/3) +
  geom_line(aes(color = Condition), size=1) +
  geom_text(data=data.frame(Intero_Regulation = -0.15, 
                            Predicted = c(0.25, 0.45, 0.75),
                            Condition = c("Polygraph", "Interrogation", "Polygraph"), 
                            Answer = c("Lie", "Lie", "Truth")),
            label = c("***", "*", "*"),
            color = c("#FF5722", "#2196F3", "#FF5722"),
            size = 10, show.legend = FALSE, fontface = "bold") +
  labs(y = "Confidence",
       x = expression(Interoception~"'Regulation'"["  (.71 MAIA Not-worrying, .61 HCT Accuracy, .40 MAIA Trusting)"])) +
  scale_y_continuous(labels = scales::percent) + 
  scale_color_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  scale_fill_manual(values = c("Polygraph" = "#FF5722", "Interrogation" = "#2196F3")) +
  facet_wrap(~Answer) +
  theme_modern(axis.title.space = 10) +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = c("grey"), color = "white")) 
p5
